\documentclass[letterpaper,11pt]{article}

\usepackage[english]{babel}
\usepackage{lmodern} % Font
\usepackage{geometry} % For margins
\usepackage{hyperref} % For clickable links
\usepackage{fontawesome5} % For icons like phone, email

% Adjust page margins
\geometry{
    a4paper,
    left=1in,
    right=1in,
    top=1in,
    bottom=1in,
}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}

\begin{document}

%------------------------------------------------
%   YOUR INFORMATION
%------------------------------------------------
\begin{center}
    \textbf{\LARGE Yashwanth Raj Tirupati}
    \vspace{4pt}
    
    \small
    \href{mailto:tyashwanth99@gmail.com}{ tyashwanth99@gmail.com }\textbar
     ~(937)-469-9700 \textbar
    \href{https://linkedin.com/in/yashwanthtirupati}{~ LinkedIn: yashwanthtirupati }\textbar 
    \href{https://github.com/proxiee}{~GitHub: proxiee }
\end{center}

\vspace{20pt}

%------------------------------------------------
%   RECIPIENT INFORMATION
%------------------------------------------------
\begin{flushleft}
    \today \\
    \vspace{12pt}
    Hiring Manager \\
    HeyGen \\
    [Location -  Obtain from Job Description if available] \\
\end{flushleft}

% \vspace{2pt}

%------------------------------------------------
%   SUBJECT LINE
%------------------------------------------------
\begin{flushleft}
\textbf{Subject: Application for Software Engineer, Dev Productivity}
\end{flushleft}


% \vspace{2pt}

%------------------------------------------------
%   LETTER CONTENT
%------------------------------------------------
\begin{flushleft}
Dear Hiring Manager,

\vspace{12pt}

I am writing to express my keen interest in the Software Engineer, Dev Productivity position at HeyGen, as advertised on [Platform - Remove this line].  HeyGen's mission to democratize visual storytelling deeply resonates with my passion for leveraging technology to enhance accessibility and efficiency.

\vspace{12pt}

My background as a Software Engineer with a Master's degree in Computer Science, coupled with my proven experience in optimizing CI/CD pipelines and developer workflows, aligns perfectly with the requirements of this role.  My expertise lies in automating processes, improving developer experience, and accelerating software delivery—all key aspects of this position.

\vspace{12pt}

My accomplishments directly address the responsibilities outlined in the job description.  For example, in my recent project, "Automated CI/CD Pipeline for Microservices," I designed and implemented a high-performance pipeline using GitHub Actions and Kubernetes, resulting in a 40\% reduction in deployment time and a 25\% increase in reliability.  Furthermore, the integration of automated testing reduced deployment failures by 30\%.  My work on "DevOps Tooling for Enhanced Developer Workflow" saw the development of internal tools using Python and Bash scripting, leading to a 20\% improvement in developer efficiency and a 50\% reduction in new developer setup time through a self-service provisioning platform.  Finally, my project, "Optimized Docker Image Builds for Faster Feedback Loops," achieved a 60\% reduction in Docker image sizes through optimized dependency management and multi-stage builds, and a doubling of concurrent builds handled after migrating to a Kubernetes-based solution.

\vspace{12pt}

My experience at Cognizant Technology Solutions further strengthens my qualifications. As a Software Developer, I improved API response times by 15\% and collaborated effectively within an Agile environment. My previous internship focused on identifying and resolving bugs, resulting in a 10\% reduction in reported issues.  These experiences demonstrate my proficiency in Python, Kubernetes, and a commitment to delivering high-quality, efficient software solutions.  My resume provides further details on my skills and accomplishments.  I am confident I can make a significant contribution to HeyGen's team and am eager to discuss how my expertise can benefit your organization.


\vspace{20pt}

Sincerely, \\
\vspace{15pt}
Yashwanth Raj Tirupati

\end{flushleft}

\end{document}