\documentclass[letterpaper,11pt]{article}

\usepackage[english]{babel}
\usepackage{lmodern} % Font
\usepackage{geometry} % For margins
\usepackage{hyperref} % For clickable links
\usepackage{fontawesome5} % For icons like phone, email

% Adjust page margins
\geometry{
    a4paper,
    left=1in,
    right=1in,
    top=1in,
    bottom=1in,
}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}

\begin{document}

%------------------------------------------------
%   YOUR INFORMATION
%------------------------------------------------
\begin{center}
    \textbf{\LARGE Yashwanth Raj Tirupati}
    \vspace{4pt}
    
    \small
    \href{mailto:tyashwanth99@gmail.com}{ tyashwanth99@gmail.com }\textbar
     ~(937)-469-9700 \textbar
    \href{https://linkedin.com/in/yashwanthtirupati}{~ LinkedIn: yashwanthtirupati }\textbar 
    \href{https://github.com/proxiee}{~GitHub: proxiee }
\end{center}

\vspace{20pt}

%------------------------------------------------
%   RECIPIENT INFORMATION
%------------------------------------------------
\begin{flushleft}
    June 22, 2025 \\
    \vspace{12pt}
    Hiring Manager \\
    Versique \\
    Twin Cities, Minnesota \\
\end{flushleft}

% \vspace{2pt}

%------------------------------------------------
%   SUBJECT LINE
%------------------------------------------------
\begin{flushleft}
\textbf{Subject: Application for Full Stack Software Engineer}
\end{flushleft}


% \vspace{2pt}

%------------------------------------------------
%   LETTER CONTENT
%------------------------------------------------
\begin{flushleft}
Dear Hiring Manager,

\vspace{12pt}

I am writing to express my keen interest in the Full Stack Software Engineer position at Versique, as advertised.  My background in full-stack development, coupled with my experience building and deploying AI-driven features, aligns perfectly with the requirements outlined in the job description. I am particularly drawn to Versique's reputation as a high-performance recruiting firm and its commitment to fostering a diverse and inclusive workforce.

\vspace{12pt}

My experience building and deploying AI-driven features for enterprise systems demonstrates my ability to translate complex user needs into efficient, robust software solutions.  For instance, during my time at Cognizant Technology Solutions, I developed and deployed full-stack features resulting in a 15% faster API response time.  Furthermore, I have consistently demonstrated expertise in optimizing on-device performance and improving model accuracy, reducing latency by 30% in my "Real-time Hand Tracking & Gesture Recognition for AR" project to enable 90 FPS performance.

\vspace{12pt}

My recent projects further highlight my capabilities.  My "AI-Powered Workflow Automation Tool" showcases my proficiency with Python (FastAPI), React, and TypeScript. This project resulted in a 20% increase in user efficiency and a 15% improvement in task completion time through the integration of an LLM-based natural language processing component.  Additionally, my experience building a "Data Processing Pipeline with ETL" using Python and PostgreSQL showcases my ability to manage large datasets efficiently, increasing processing speed by 3x.  This experience directly complements the requirements outlined in the job description regarding experience with PostgreSQL and ETL processes.

\vspace{12pt}

I am confident that my skills and experience in Python, React, TypeScript, FastAPI, and PostgreSQL, combined with my demonstrated success in AI-driven projects, make me a strong candidate for this position. My resume provides further details on my qualifications, and I am eager to discuss how my contributions can benefit your team.  Thank you for your time and consideration.

\vspace{20pt}

Sincerely, \\
% \vspace{15pt}
Yashwanth Raj Tirupati

\end{flushleft}

\end{document}