\documentclass[letterpaper,11pt]{article}

\usepackage[english]{babel}
\usepackage{lmodern} % Font
\usepackage{geometry} % For margins
\usepackage{hyperref} % For clickable links
\usepackage{fontawesome5} % For icons like phone, email

% Adjust page margins
\geometry{
    a4paper,
    left=1in,
    right=1in,
    top=1in,
    bottom=1in,
}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}

\begin{document}

%------------------------------------------------
%   YOUR INFORMATION
%------------------------------------------------
\begin{center}
    \textbf{\LARGE Yashwanth Raj Tirupati}
    \vspace{4pt}
    
    \small
    \href{mailto:tyashwanth99@gmail.com}{ tyashwanth99@gmail.com }\textbar
     ~(937)-469-9700 \textbar
    \href{https://linkedin.com/in/yashwanthtirupati}{~ LinkedIn: yashwanthtirupati }\textbar 
    \href{https://github.com/proxiee}{~GitHub: proxiee }
\end{center}

\vspace{20pt}

%------------------------------------------------
%   RECIPIENT INFORMATION
%------------------------------------------------
\begin{flushleft}
    June 23, 2025 \\
    \vspace{12pt}
    Hiring Manager \\
\end{flushleft}

% \vspace{2pt}

%------------------------------------------------
%   SUBJECT LINE
%------------------------------------------------
\begin{flushleft}
\textbf{Subject: Application for Software Engineer 2}
\end{flushleft}


% \vspace{2pt}

%------------------------------------------------
%   LETTER CONTENT
%------------------------------------------------
\begin{flushleft}
Dear Hiring Manager,

\vspace{12pt}

I am writing to express my keen interest in the Software Engineer 2 position.  My background as a results-driven Software Engineer with an M.S. in Computer Science aligns perfectly with the requirements outlined in the job description. My expertise in developing and deploying high-quality, maintainable software, particularly using Java, Python, and C++, makes me a strong candidate for this role.

\vspace{12pt}

My experience at Cognizant Technology Solutions further solidified my skills in full-stack development and Agile methodologies.  During my time as a Software Developer, I developed and deployed 5 full-stack features for enterprise systems using Spring Boot (Java) and modern front-end frameworks, resulting in extensible and maintainable code.  Furthermore, my collaboration with stakeholders to translate user requirements into technical specifications improved API response times by 15\%. As a Programmer Analyst Intern, I identified and resolved 100+ bugs, resulting in a 10\% reduction in reported issues. I also improved code quality and reliability through technical documentation and enhanced test automation.


\vspace{12pt}

My personal projects demonstrate my commitment to continuous learning and innovation.  In my "Real-time Hand Tracking & Gesture Recognition for AR" project, I developed a deep learning model (C++, PyTorch) achieving 98.5\% accuracy on a dataset of 50 complex gestures.  Through architectural engineering and data augmentation, I reduced latency by 30\% and increased model robustness by 25\%, achieving 90 FPS on-device performance.  My work on "Enterprise-Level Software System Enhancement" resulted in a 20\% reduction in processing time and a 15\% decrease in resource consumption by refactoring core components.  I also implemented a new monitoring system that reduced error rates by 10\%, facilitating proactive issue resolution. Finally, my "Automated Code Quality Improvement System" identified and flagged 80\% of common code quality issues, saving 10 hours per week in manual review time and reducing bug occurrences by 5\% after integration into the CI/CD pipeline.


\vspace{12pt}

These achievements showcase my proficiency in software development, problem-solving, and my dedication to enhancing code quality and system performance—all crucial aspects of the Software Engineer 2 role. My resume provides further details on my qualifications and accomplishments. I am confident I possess the technical skills and collaborative spirit to make significant contributions to your team.  Thank you for your time and consideration. I look forward to hearing from you soon.


\vspace{20pt}

Sincerely, \\
% \vspace{15pt}
Yashwanth Raj Tirupati

\end{flushleft}

\end{document}