\documentclass[letterpaper,11pt]{article}

\usepackage[english]{babel}
\usepackage{lmodern} % Font
\usepackage{geometry} % For margins
\usepackage{hyperref} % For clickable links
\usepackage{fontawesome5} % For icons like phone, email

% Adjust page margins
\geometry{
    a4paper,
    left=1in,
    right=1in,
    top=1in,
    bottom=1in,
}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}

\begin{document}

%------------------------------------------------
%   YOUR INFORMATION
%------------------------------------------------
\begin{center}
    \textbf{\LARGE Yashwanth Raj Tirupati}
    \vspace{4pt}
    
    \small
    \href{mailto:tyashwanth99@gmail.com}{ tyashwanth99@gmail.com }\textbar
     ~(937)-469-9700 \textbar
    \href{https://linkedin.com/in/yashwanthtirupati}{~ LinkedIn: yashwanthtirupati }\textbar 
    \href{https://github.com/proxiee}{~GitHub: proxiee }
\end{center}

\vspace{20pt}

%------------------------------------------------
%   RECIPIENT INFORMATION
%------------------------------------------------
\begin{flushleft}
    June 22, 2025 \\
    \vspace{12pt}
    Hiring Manager \\
    FinconsUS \\
    Downtown Los Angeles, CA \\
\end{flushleft}

% \vspace{2pt}

%------------------------------------------------
%   SUBJECT LINE
%------------------------------------------------
\begin{flushleft}
\textbf{Subject: Application for Full-Stack Java/Node.js Engineer}
\end{flushleft}


% \vspace{2pt}

%------------------------------------------------
%   LETTER CONTENT
%------------------------------------------------
\begin{flushleft}
Dear Hiring Manager,

\vspace{12pt}

I am writing to express my keen interest in the Full-Stack Java/Node.js Engineer position at FinconsUS, as advertised.  My experience in developing and optimizing scalable applications, coupled with my proficiency in Java, Node.js, and modern front-end frameworks, aligns strongly with the requirements outlined in the job description.

\vspace{12pt}

My background includes two years of experience at Cognizant Technology Solutions, where I honed my full-stack development skills, and significantly improved API response times by 15% during my tenure as a Software Developer.  This involved developing and deploying full-stack features for enterprise systems using Spring Boot and modern front-end frameworks.  Prior to that, as a Programmer Analyst Intern, I reduced reported issues by 10% for key modules by proactively identifying and resolving bugs.

\vspace{12pt}

Beyond my professional experience, my personal projects showcase my ability to deliver high-performance solutions.  My "Scalable E-commerce Platform using Java and React" project, for instance, supports 10,000 concurrent users with an average response time under 200ms. This project also achieved a 30% reduction in infrastructure costs through the implementation of RESTful APIs and a microservices architecture.  Furthermore, my "Microservices-based Streaming Service" project, built using Node.js and a NoSQL database, handles 500 concurrent streams with minimal latency and resulted in a 20% increase in user engagement through well-designed RESTful API endpoints.

\vspace{12pt}

These achievements demonstrate my expertise in Java, Node.js, RESTful API design, microservices, SQL and NoSQL databases, and my commitment to building high-performance, scalable applications. My  proficiency in these areas directly addresses FinconsUS's need for a skilled full-stack engineer. I am confident I can make a significant contribution to your team and am eager to discuss my qualifications further.  My resume provides further details on my experience and skills.

\vspace{20pt}

Sincerely, \\
\vspace{15pt}
Yashwanth Raj Tirupati

\end{flushleft}

\end{document}