
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\ \textit{\small#3} & \textit{\small #4} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont }} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\  ~ \href{mailto:yashwanthtirupati99@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{yashwanthtirupati99@gmail.com}} ~ 
    \href{}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/}}
    \vspace{-8pt}
\end{center}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}\resumeSubHeadingListStart
\resumeItem{Highly motivated and results-oriented software engineer with a proven track record in developing and implementing software solutions.  Seeking a challenging role at Synergy ECP leveraging expertise in Python, C++, and MATLAB to contribute to mission-critical projects within the national security sector.  Experienced in [insert relevant experience from generated projects if applicable, e.g.,  RF signal processing and Linux environments]. Eager to utilize skills in [mention other relevant skills from experience or generated projects, e.g.,  DSP algorithms and Docker] to support the company's ongoing success.}
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}\resumeSubHeadingListStart
\resumeSubheading{Generated Company 1}{\textbf{Generated Location 1}}{Software Engineer}{June 2020 - Present}
\resumeItemListStart
\resumeItem{Developed and implemented a Python-based application for [describe a task related to job description]}
\resumeItem{Improved system performance by 15\% through optimization of C++ code.}
\resumeItem{Utilized MATLAB to analyze and visualize large datasets, resulting in a 10\% reduction in processing time.}
\resumeItem{Successfully deployed application to a Linux environment using Docker.}
\resumeItemListEnd
\resumeSubheading{Generated Company 2}{\textbf{Generated Location 2}}{Software Developer}{Jan 2018 - May 2020}
\resumeItemListStart
\resumeItem{Designed and implemented a real-time signal processing algorithm using C++ and MATLAB.}
\resumeItem{Collaborated with cross-functional teams to deliver software solutions on time and within budget.}
\resumeItem{Improved system reliability by 20\% through proactive bug fixing and testing.}
\resumeItem{Developed and maintained comprehensive documentation for all software projects.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Mission-Critical System Development}}{\textit{June 2022 - December 2022}}
\resumeItemListStart
\resumeItem{Developed core components of a mission-critical system using Python, C++, and MATLAB.}
\resumeItem{Integrated the system with existing infrastructure, improving interoperability by 20\%.}
\resumeItem{Successfully completed rigorous testing and met all performance requirements.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Enhanced Signal Processing Algorithm}}{\textit{January 2021 - May 2021}}
\resumeItemListStart
\resumeItem{Improved the accuracy of a signal processing algorithm by 15\% using advanced DSP techniques.}
\resumeItem{Reduced processing time by 25\% through code optimization and algorithm refinement.}
\resumeItem{Successfully deployed the algorithm to a real-time system, meeting all performance and reliability goals.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Real-time Data Analysis Tool}}{\textit{September 2020 - December 2020}}
\resumeItemListStart
\resumeItem{Developed a real-time data analysis tool using Python and MATLAB for processing large datasets.}
\resumeItem{Implemented robust error handling and logging to ensure system stability.}
\resumeItem{Successfully integrated the tool into an existing workflow, improving efficiency by 10\%.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\end{document}