
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont sjdhfl;kjasdlj}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 9375678888 ~ \href{mailto:testing@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{testing@gmail.com}} ~ 
    \href{https://www.linkedin.com/feed/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}\resumeSubHeadingListStart
\resumeItem{Senior Developer with 7+ years' experience delivering business-critical software to large enterprises.  Proficient in Django/Flask, Power BI/PowerApps/Azure.  Expert in API specification, development, and long-term maintenance. Seeking a challenging, remote role.}
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}\resumeSubHeadingListStart
\resumeSubheading{sdhfkljsdahfjksha}{\textbf{jhdkljfhkljshdfkj}}{jhdfjklhasjkhdfkljhasd}{hkdjhfsha}
\resumeItemListStart
\resumeItem{hjksdfhkjshdfkjhasdjkfhkjasdhfkjasdhfkljsdhakfbksdjahfjksdh}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}\resumeSubHeadingListStart
\resumeSubheading{Example Company}{\textbf{Remote}}{Senior Software Engineer}{2016-2023}
\resumeItemListStart
\resumeItem{Led development of a new customer-facing API, resulting in a 20\% increase in transaction volume.}
\resumeItem{Architected and implemented a microservices-based system, improving system scalability by 30\%.}
\resumeItem{Mentored junior engineers, fostering a collaborative and high-performing team environment.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Enterprise Logistics Platform}}{\textit{2021-2023}}
\resumeItemListStart
\resumeItem{Developed a scalable, high-performance logistics platform for a Fortune 500 company using Django and Azure.}
\resumeItem{Implemented robust security measures, ensuring compliance with industry regulations (PCI DSS).}
\resumeItem{Improved data processing efficiency by 15\% through optimized database queries and caching strategies.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{FinTech Transaction Processing System}}{\textit{2019-2021}}
\resumeItemListStart
\resumeItem{Designed and implemented a real-time transaction processing system for a leading FinTech firm using Flask and Power BI for data visualization.}
\resumeItem{Reduced transaction processing time by 25\% through performance optimization and code refactoring.}
\resumeItem{Successfully integrated the system with multiple third-party APIs, ensuring seamless data exchange.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Insurance Claims Processing Application}}{\textit{2017-2019}}
\resumeItemListStart
\resumeItem{Built a user-friendly insurance claims processing application using PowerApps, improving user satisfaction by 18\%.}
\resumeItem{Automated key processes, reducing manual effort by 40\% and increasing throughput.}
\resumeItem{Implemented comprehensive data security measures, ensuring compliance with HIPAA regulations.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SKILLS}}}\resumeSubHeadingListStart
\resumeItem{\textbf{jksdfhjksadhfk:} hkjdfkjashdfjkhds}
\resumeSubHeadingListEnd\vspace{-10pt}
\end{document}