
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\ \textit{\small#3} & \textit{\small #4} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont Sanaharika Thallada}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 217-775-5653 ~ \href{mailto:sanaharikathallada@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{sanaharikathallada@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/yashwanthtirupati/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}\resumeSubHeadingListStart
\resumeItem{Full-stack engineer with experience in Java and Typescript, seeking to leverage skills in building reliable, secure software systems for impactful projects.}
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}\resumeSubHeadingListStart
\resumeSubheading{Saint Louis University}{\textbf{Saint Louis, Missouri}}{Master of Science, Information Systems}{Aug 2023 – May2025}
\resumeItemListStart
\resumeItem{CGPA: 3.63/4.0}
\resumeItem{Coursework: Mobile \&Web App Development, Data Visualization \& Analysis, AWS, Statistics, Tech\& Start-ups}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}\resumeSubHeadingListStart
\resumeSubheading{Cognizant Technology Solutions | Titan}{\textbf{Hyderabad}}{Full-Stack Java Developer}{Aug 2020 – Jul 2023}
\resumeItemListStart
\resumeItem{Developed and deployed highly reliable Java-based microservices for a large-scale application processing terabytes of data daily.}
\resumeItem{Improved application performance by 20\% through code optimization and database tuning, resulting in significant cost savings.}
\resumeItem{Collaborated with cross-functional teams to design, develop, and test new features, ensuring timely delivery and high-quality results.}
\resumeItem{Utilized Agile methodologies (Scrum) throughout the software development lifecycle, consistently exceeding project expectations.}
\resumeItemListEnd
\resumeSubheading{Cognizant Technology Solutions}{\textbf{Pune, Maharastra}}{Intern – Programmer Analyst}{Jan 2020 – May 2020}
\resumeItemListStart
\resumeItem{Contributed to the development of a web application using Java and Spring Boot, enhancing user experience and improving data management.}
\resumeItem{Successfully implemented a new algorithm that improved data processing speed by 15\%, leading to increased efficiency.}
\resumeItem{Collaborated with senior developers to troubleshoot and resolve critical issues, demonstrating strong problem-solving skills.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Secure Satellite Network Communication System}}{\textit{March 2023 - October 2023}}
\resumeItemListStart
\resumeItem{Designed and implemented a secure communication system for a network of 100+ satellites using C\# and Typescript, ensuring reliable data transmission in low earth orbit.}
\resumeItem{Developed and integrated a real-time data processing pipeline to handle high-volume data streams from remote sensors, leveraging cloud infrastructure (AWS).}
\resumeItem{Employed advanced encryption techniques and security protocols to protect sensitive data, adhering to strict government regulations.}
\resumeItem{Reduced latency by 10\% through efficient data compression and optimized network protocols.}
\resumeItem{Utilized Kubernetes for container orchestration, enhancing scalability and resilience of the system.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Immersive Earth Observation Platform}}{\textit{September 2022 - February 2023}}
\resumeItemListStart
\resumeItem{Developed a web application using Typescript and React that provides an immersive visualization experience for earth observation data.}
\resumeItem{Integrated PostgreSQL for efficient management of large image datasets, ensuring fast query response times.}
\resumeItem{Implemented advanced image processing algorithms for enhanced data analysis, incorporating machine learning techniques for improved accuracy.}
\resumeItem{Deployed the application to AWS, utilizing serverless technologies to optimize cost and scalability.}
\resumeItem{Improved user engagement by 15\% through intuitive design and user-friendly interface.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Real-time Data Processing Pipeline}}{\textit{May 2022 - December 2022}}
\resumeItemListStart
\resumeItem{Built a real-time data processing pipeline using C\# and Kafka to process sensor data from multiple sources.}
\resumeItem{Developed algorithms for data cleaning, transformation, and aggregation to ensure data quality.}
\resumeItem{Implemented a system for alerting and notification to provide immediate feedback on anomalies.}
\resumeItem{Improved data processing speed by 25\% through efficient algorithm design and optimization.}
\resumeItem{Successfully integrated the pipeline with various downstream systems.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SKILLS}}}\resumeSubHeadingListStart
\resumeItem{\textbf{Languages \& Frameworks:} Java, C, C++, Spring Boot, Hibernate, Angular2/4/8, React, Node.js, JSP, Servlets, MVC}\vspace{-7pt}
\resumeItem{\textbf{Frontend:} HTML5, CSS3, JavaScript, jQuery, JSON, XML, XSLT}\vspace{-7pt}
\resumeItem{\textbf{Web Services:} REST , SOAP}\vspace{-7pt}
\resumeItem{\textbf{Cloud \&DevOps:} AWS, Azure, Docker, Google cloud,}\vspace{-7pt}
\resumeItem{\textbf{Tools:} Jira, Confluence, GitHub,GitLab, Postman, Elasticsearch}\vspace{-7pt}
\resumeItem{\textbf{Database:} MySQL}\vspace{-7pt}
\resumeItem{\textbf{Messaging Queues:} ActiveMQ, RabbitMQ}\vspace{-7pt}
\resumeItem{\textbf{Security:} OAuth2, JWT, Spring Security}
\resumeSubHeadingListEnd\vspace{-10pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{CERTIFICATIONS ( UDEMY)}}}
\resumeItemListStart
\resumeItem{Agile Project Management}
\resumeItem{Relational Database Design}
\resumeItem{Responsive Web Design}
\resumeItem{Java Database Connection}
\resumeItem{Maven Crash Course}
\resumeItem{Spring Framework}
\resumeItem{Build Java app with Spring MVC}
\resumeItemListEnd
\vspace{-10pt}
\end{document}