
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\ \textit{\small#3} & \textit{\small #4} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont }} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\  ~ \href{mailto:yashwanthtirupati99@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{yashwanthtirupati99@gmail.com}} ~ 
    \href{}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/}}
    \vspace{-8pt}
\end{center}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}\resumeSubHeadingListStart
\resumeItem{Highly motivated and results-oriented Software Engineer with a proven track record in developing and implementing software solutions.  Seeking a challenging role at Synergy where I can leverage my expertise in Python, C++, and MATLAB to contribute to mission-critical projects within the National Security sector.  Experienced in [insert relevant experience from generated projects if applicable, e.g.,  signal processing algorithms and Linux environments]. Eager to collaborate with a skilled team and contribute to the company's continued success.}
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}\resumeSubHeadingListStart
\resumeSubheading{Generated Company 1}{\textbf{Generated Location 1}}{Software Engineer}{June 2020 - Present}
\resumeItemListStart
\resumeItem{Developed and implemented a Python-based application for real-time data analysis, resulting in a 15\% increase in processing speed.}
\resumeItem{Designed and implemented a C++ module for signal processing, improving accuracy by 10\%.}
\resumeItem{Utilized MATLAB for algorithm development and testing, leading to a 20\% reduction in error rates.}
\resumeItemListEnd
\resumeSubheading{Generated Company 2}{\textbf{Generated Location 2}}{Software Developer}{August 2018 - June 2020}
\resumeItemListStart
\resumeItem{Developed and maintained software applications using Python, C++, and MATLAB.}
\resumeItem{Collaborated with cross-functional teams to design and implement new features.}
\resumeItem{Improved code efficiency by 25\% through refactoring and optimization.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Real-time Data Processing System}}{\textit{June 2022 - December 2022}}
\resumeItemListStart
\resumeItem{Developed a real-time data processing system using Python and C++ to handle high-volume data streams.}
\resumeItem{Implemented signal processing algorithms using MATLAB to extract relevant information from noisy data.}
\resumeItem{Deployed the system on a Linux server using Docker containers for scalability and reliability.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Signal Processing Algorithm Development}}{\textit{January 2022 - May 2022}}
\resumeItemListStart
\resumeItem{Developed and implemented a new signal processing algorithm using MATLAB to improve the accuracy of data analysis.}
\resumeItem{Reduced processing time by 15\% through algorithm optimization.}
\resumeItem{Tested the algorithm on various datasets to ensure accuracy and robustness.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{RF Signal Analysis Tool}}{\textit{September 2021 - December 2021}}
\resumeItemListStart
\resumeItem{Developed a tool for analyzing RF signals using Python and C++.}
\resumeItem{Integrated the tool with a Linux-based system for real-time data analysis.}
\resumeItem{Improved the efficiency of the signal analysis process by 20\%.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\end{document}