
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
% Page Style
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
% URL Style
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\pdfgentounicode=1
% Spacing
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}
% Document Start
\begin{document}


% --- HEADER ---
\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont Sanaharika Thallada}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 217-775-5653 ~ \href{mailto:sanaharikathallada@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{sanaharikathallada@gmail.com}} ~
    \href{https://www.linkedin.com/in/yashwanthtirupati/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
\end{center}
\vspace{0.5cm}

June 23, 2025

Hiring Manager
Finance of America Holdings LLC


I am writing to express my keen interest in the Python Developer II position, as posted on your job board.  My three plus years of experience as a Full-Stack Java Developer, coupled with my passion for Python and cloud technologies, align perfectly with the requirements outlined in the job description.  During my tenure at Cognizant Technology Solutions, I consistently exceeded expectations, contributing significantly to the enhancement and optimization of software development processes. For instance, I spearheaded the development of key features for a large-scale Java application, resulting in a fifteen percent increase in user engagement.  This success stemmed from my focus on creating intuitive and user-friendly interfaces.


My experience extends beyond Java.  I have independently developed several projects showcasing my proficiency in Python.  Specifically, my work on an e-commerce platform, using the Python and Django framework, resulted in a thirty percent improvement in site performance through strategic code optimization and caching strategies. This project further honed my skills in payment gateway integration and implementing robust APIs, directly relevant to the responsibilities outlined in the position description.  Furthermore, my creation of a data analytics dashboard using Python, Pandas, and NumPy, and integrated with AWS cloud services, demonstrates my ability to leverage data for actionable insights—a critical skill for contributing to your analytics program.


Beyond technical expertise, I am adept at working collaboratively within cross-functional teams and providing constructive feedback to junior team members. My experience at Cognizant Technology Solutions involved frequent collaboration and mentorship, fostering a team-oriented approach crucial for a successful working environment.  I am also experienced in object-oriented programming, scalable data application design, containerization (Docker and Kubernetes), CI/CD pipelines, testing frameworks (including PyTest), data libraries (Pandas, NumPy, and scikit-learn), AWS cloud compute (ECS and Lambda), databases (PostgreSQL and MSSQL), REST APIs, and microservice architecture—all crucial skills listed in your requirements.


I am confident that my blend of technical skills, proven track record of success, and commitment to continuous learning makes me a strong candidate for this role. I am eager to contribute to Finance of America Holdings LLC and am excited about the opportunity to discuss my qualifications further.


Sincerely,

Sanaharika Thallada
\end{document}