
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont sjdhfl;kjasdlj}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 9375678888 ~ \href{mailto:testing@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{testing@gmail.com}} ~ 
    \href{https://www.linkedin.com/feed/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}


\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}
\resumeSubHeadingListStart

\resumeItem{Senior Developer with 7+ years' experience delivering business-critical software to large enterprises.  Proficient in Django/Flask, Power BI/PowerApps/Azure.  Expert in API specification, development, and long-term maintenance.  Seeking a challenging remote role.}
\resumeSubHeadingListEnd
\vspace{-18pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}
\resumeSubHeadingListStart
\resumeSubheading{sdhfkljsdahfjksha}{\textbf{jhdkljfhkljshdfkj}}{jhdfjklhasjkhdfkljhasd}{hkdjhfsha}
\resumeItemListStart
\resumeItem{hjksdfhkjshdfkjhasdjkfhkjasdhfkjasdhfkljsdhakfbksdjahfjksdh}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-18pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}
\resumeSubHeadingListStart
\resumeSubheading{sdjhfasdhf}{\textbf{sdkjahfsdhf}}{Senior Software Developer}{3874sdfh}
\resumeItemListStart
\resumeItem{Developed and maintained 3 key features for a flagship product, resulting in a 15\% increase in user engagement.}
\resumeItem{Led a team of 5 developers in the migration of a legacy system to a cloud-based architecture, reducing infrastructure costs by 20\%.}
\resumeItem{Designed and implemented 5 new APIs, improving system scalability and reducing latency by 30\%.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-17pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Enterprise Logistics Platform}}{\textit{2021-2023}}
\resumeItemListStart
\resumeItem{Developed a scalable Django-based platform for a Fortune 500 logistics company, handling 100M+ transactions annually.}
\resumeItem{Integrated Power BI dashboards for real-time performance monitoring and data-driven decision-making.}
\resumeItem{Utilized Azure cloud services for high availability and disaster recovery, ensuring 99.9\% uptime.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{FinTech Transaction Processing System}}{\textit{2019-2021}}
\resumeItemListStart
\resumeItem{Built a high-throughput Flask application for processing financial transactions, achieving a 99.99\% success rate.}
\resumeItem{Implemented robust security measures to protect sensitive data, exceeding industry compliance standards.}
\resumeItem{Improved system performance by 40\% through code optimization and database tuning.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Insurance Claims Processing System}}{\textit{2017-2019}}
\resumeItemListStart
\resumeItem{Designed and developed a new API for processing insurance claims, reducing processing time by 25\%.}
\resumeItem{Created PowerApps solution for streamlined user interaction and claim submission.}
\resumeItem{Integrated the system with existing legacy systems, ensuring seamless data exchange.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-17pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SKILLS}}}
\resumeSubHeadingListStart
\resumeItem{\textbf{jksdfhjksadhfk:} hkjdfkjashdfjkhds}
\resumeSubHeadingListEnd
\vspace{-10pt}
\end{document}