
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont sjdhfl;kjasdlj}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 9375678888 ~ \href{mailto:testing@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{testing@gmail.com}} ~ 
    \href{https://www.linkedin.com/feed/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}\resumeSubHeadingListStart
\resumeItem{Data-driven analyst with proven ability to source, compile, and interpret data to produce insightful reports.  Proficient in data analysis techniques and adept at presenting findings to stakeholders. Seeking to leverage skills in a challenging role.}
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}\resumeSubHeadingListStart
\resumeSubheading{sdhfkljsdahfjksha}{\textbf{jhdkljfhkljshdfkj}}{jhdfjklhasjkhdfkljhasd}{hkdjhfsha}
\resumeItemListStart
\resumeItem{hjksdfhkjshdfkjhasdjkfhkjasdhfkjasdhfkljsdhakfbksdjahfjksdh}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}\resumeSubHeadingListStart
\resumeSubheading{Example Company}{\textbf{Example City, State}}{Data Analyst}{2020-2023}
\resumeItemListStart
\resumeItem{Developed and maintained 5 key performance indicator (KPI) dashboards, resulting in a 10\% improvement in operational efficiency.}
\resumeItem{Conducted in-depth data analysis using SQL and Python, identifying trends that informed strategic decision-making.}
\resumeItem{Collaborated with cross-functional teams to gather data requirements and translate them into actionable reports, delivered 20+ reports monthly to stakeholders}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Sales Performance Analysis}}{\textit{2022}}
\resumeItemListStart
\resumeItem{Analyzed sales data from multiple sources (CRM, ERP) to identify top-performing products and regions.}
\resumeItem{Developed a predictive model using machine learning to forecast future sales with 90\% accuracy.}
\resumeItem{Presented findings and recommendations to executive leadership resulting in a 15\% increase in sales strategy efficacy.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Customer Churn Prediction}}{\textit{2021}}
\resumeItemListStart
\resumeItem{Built a predictive model to identify at-risk customers using statistical modeling techniques (logistic regression).}
\resumeItem{Reduced customer churn rate by 5\% through targeted retention strategies based on model predictions.}
\resumeItem{Improved customer satisfaction scores by 10\% via enhanced communication based on identified customer needs.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Marketing Campaign Optimization}}{\textit{2020}}
\resumeItemListStart
\resumeItem{Analyzed marketing campaign data to identify key drivers of campaign success and areas for improvement.}
\resumeItem{Optimized marketing campaigns, increasing conversion rates by 8\% through targeted ad spend and refined messaging.}
\resumeItem{Improved return on investment (ROI) for marketing campaigns by 12\% based on data-driven optimizations.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SKILLS}}}\resumeSubHeadingListStart
\resumeItem{\textbf{jksdfhjksadhfk:} hkjdfkjashdfjkhds}
\resumeSubHeadingListEnd\vspace{-10pt}
\end{document}