
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont sjdhfl;kjasdlj}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 9375678888 ~ \href{mailto:testing@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{testing@gmail.com}} ~ 
    \href{https://www.linkedin.com/feed/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}


\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}
\resumeSubHeadingListStart

\resumeItem{Full-stack developer proficient in C\#, Angular 11+, and cloud technologies (AWS/Azure/GCP).  Experienced in designing, developing, and deploying scalable, high-performance applications using Kubernetes and Docker.  Adept at agile development and CI/CD practices.}
\resumeSubHeadingListEnd
\vspace{-18pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}
\resumeSubHeadingListStart
\resumeSubheading{sdhfkljsdahfjksha}{\textbf{jhdkljfhkljshdfkj}}{jhdfjklhasjkhdfkljhasd}{hkdjhfsha}
\resumeItemListStart
\resumeItem{hjksdfhkjshdfkjhasdjkfhkjasdhfkjasdhfkljsdhakfbksdjahfjksdh}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-18pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}
\resumeSubHeadingListStart
\resumeSubheading{Acme Corporation}{\textbf{San Francisco, CA}}{Software Engineer}{2020-2023}
\resumeItemListStart
\resumeItem{Developed and maintained 3 key features for a flagship product using Angular 11+, resulting in a 20\% increase in user engagement.}
\resumeItem{Implemented RESTful APIs using C\# and .NET, improving API response times by 15\%.}
\resumeItem{Deployed and managed applications on AWS using Kubernetes and Docker, achieving 99.99\% uptime.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-17pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{E-commerce Platform}}{\textit{2022}}
\resumeItemListStart
\resumeItem{Developed a scalable e-commerce platform using Angular 11+ for the front-end and C\#/.NET for the back-end, resulting in a 10\% increase in sales.}
\resumeItem{Implemented a robust payment gateway integration, improving transaction success rate by 5\%.}
\resumeItem{Deployed the application on AWS using Kubernetes for high availability and scalability.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Microservices Architecture Implementation}}{\textit{2021}}
\resumeItemListStart
\resumeItem{Refactored a monolithic application into a microservices architecture using Docker and Kubernetes, improving application performance by 30\%.}
\resumeItem{Reduced infrastructure costs by 15\% through optimized resource allocation.}
\resumeItem{Improved application scalability by 20\%.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Cloud-Based Inventory Management System}}{\textit{2020}}
\resumeItemListStart
\resumeItem{Designed and developed a cloud-based inventory management system using C\# and .NET, resulting in a 25\% reduction in inventory errors.}
\resumeItem{Improved data accuracy by 15\% through automated data validation.}
\resumeItem{Integrated the system with existing ERP software, improving data synchronization by 20\%.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-17pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SKILLS}}}
\resumeSubHeadingListStart
\resumeItem{\textbf{jksdfhjksadhfk:} hkjdfkjashdfjkhds}
\resumeSubHeadingListEnd
\vspace{-10pt}
\end{document}