
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont sjdhfl;kjasdlj}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 9375678888 ~ \href{mailto:testing@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{testing@gmail.com}} ~ 
    \href{https://www.linkedin.com/feed/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}\resumeSubHeadingListStart
\resumeItem{Full-stack Lead Engineer with 5+ years' experience architecting and scaling distributed systems.  Proficient in JavaScript/TypeScript, Node.js, React, and REST/WebSocket APIs.  Seeking to lead development of real-time, spatial computing applications.}
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}\resumeSubHeadingListStart
\resumeSubheading{sdhfkljsdahfjksha}{\textbf{jhdkljfhkljshdfkj}}{jhdfjklhasjkhdfkljhasd}{hkdjhfsha}
\resumeItemListStart
\resumeItem{hjksdfhkjshdfkjhasdjkfhkjasdhfkjasdhfkljsdhakfbksdjahfjksdh}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}\resumeSubHeadingListStart
\resumeSubheading{Previous Company Name}{\textbf{Previous Location}}{Senior Full-Stack Engineer}{YYYY-YYYY}
\resumeItemListStart
\resumeItem{Led development of a real-time collaboration platform using Node.js, React, and WebSockets, resulting in a 20\% increase in user engagement.}
\resumeItem{Designed and implemented REST APIs for a high-traffic application, improving response times by 15\%.}
\resumeItem{Architected and deployed a microservices-based system using Docker and Kubernetes, enhancing scalability and reducing downtime by 10\%.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Real-time Spatial Logic Engine (Bubblzz-inspired)}}{\textit{YYYY-YYYY}}
\resumeItemListStart
\resumeItem{Developed a real-time spatial logic engine using Node.js and a NoSQL database (e.g., MongoDB) to manage and coordinate objects, users, and behaviors in a simulated 3D environment.}
\resumeItem{Implemented WebSocket communication for real-time updates and interaction, achieving sub-second latency.}
\resumeItem{Designed and implemented a system for managing user permissions and dynamic interactions within the spatial environment, supporting 1000+ concurrent users.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Interactive Environment Creation Platform (AirScene-inspired)}}{\textit{YYYY-YYYY}}
\resumeItemListStart
\resumeItem{Built a platform for designing, scripting, and deploying interactive environments using React and a graph database (e.g., Neo4j) to model relationships between objects and events.}
\resumeItem{Developed an event-driven architecture using Kafka to handle real-time updates and trigger actions within the environment.}
\resumeItem{Integrated with a 3D modeling library (e.g., Three.js) to create visually rich and engaging experiences.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Mobile/Web Interface for Spatial Experiences (LightPlay-inspired)}}{\textit{YYYY-YYYY}}
\resumeItemListStart
\resumeItem{Created a mobile and web interface using React Native and React to allow users to interact with the spatial environments in real-time.}
\resumeItem{Implemented real-time collaboration features, allowing multiple users to interact simultaneously within the same environment.}
\resumeItem{Integrated user authentication and authorization mechanisms using OAuth 2.0, ensuring secure and controlled access to the platform.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SKILLS}}}\resumeSubHeadingListStart
\resumeItem{\textbf{jksdfhjksadhfk:} hkjdfkjashdfjkhds}
\resumeSubHeadingListEnd\vspace{-10pt}
\end{document}