
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont sjdhfl;kjasdlj}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 9375678888 ~ \href{mailto:testing@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{testing@gmail.com}} ~ 
    \href{https://www.linkedin.com/feed/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}\resumeSubHeadingListStart
\resumeItem{Highly skilled Senior Front-End Engineer with 5+ years of experience designing and developing high-performance, responsive web interfaces using React and Angular. Proven ability to integrate front-end code with back-end APIs, optimize for speed, and ensure accessibility (WCAG 2.1). Expertise in CSS preprocessors, design tools (Figma, Sketch), and version control (Git).  Adept at collaborating with cross-functional teams to deliver exceptional user experiences.}
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}\resumeSubHeadingListStart
\resumeSubheading{sdhfkljsdahfjksha}{\textbf{jhdkljfhkljshdfkj}}{jhdfjklhasjkhdfkljhasd}{hkdjhfsha}
\resumeItemListStart
\resumeItem{hjksdfhkjshdfkjhasdjkfhkjasdhfkjasdhfkljsdhakfbksdjahfjksdh}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}\resumeSubHeadingListStart
\resumeSubheading{Previous Company Name}{\textbf{Previous Location}}{Senior Front End Engineer}{YYYY-YYYY}
\resumeItemListStart
\resumeItem{Developed and maintained 15+ responsive web applications using React, resulting in a 20\% increase in user engagement.}
\resumeItem{Improved website load times by 30\% through performance optimization techniques, leading to a 15\% increase in conversion rates.}
\resumeItem{Collaborated with UX designers and backend developers to implement pixel-perfect, accessible interfaces adhering to WCAG 2.1 guidelines.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{High-Performance Investment Dashboard}}{\textit{YYYY-YYYY}}
\resumeItemListStart
\resumeItem{Developed a React-based dashboard providing real-time financial data visualization for high-net-worth clients, resulting in a 10\% increase in client satisfaction.}
\resumeItem{Integrated with RESTful APIs to fetch and display market data, achieving sub-second response times and 99.9\% uptime.}
\resumeItem{Implemented responsive design and accessibility features (WCAG 2.1) ensuring usability across devices.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Cloud-Native Insurance Platform UI}}{\textit{YYYY-YYYY}}
\resumeItemListStart
\resumeItem{Designed and built a user-friendly UI for a cloud-native insurance platform, improving user onboarding by 15\%.}
\resumeItem{Utilized Angular and Tailwind CSS for efficient development and consistent styling across the platform.}
\resumeItem{Integrated with GraphQL APIs for seamless data retrieval and optimized performance.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{AI-Powered Customer Acquisition Platform}}{\textit{YYYY-YYYY}}
\resumeItemListStart
\resumeItem{Created a dynamic, responsive UI for an AI-driven customer acquisition platform, leveraging machine learning algorithms.}
\resumeItem{Improved the platform's conversion rate by 25\% through optimized UI/UX design and A/B testing.}
\resumeItem{Implemented a robust component library using React and Material-UI, ensuring consistent design across modules.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SKILLS}}}\resumeSubHeadingListStart
\resumeItem{\textbf{jksdfhjksadhfk:} hkjdfkjashdfjkhds}
\resumeSubHeadingListEnd\vspace{-10pt}
\end{document}