
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont sjdhfl;kjasdlj}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 9375678888 ~ \href{mailto:testing@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{testing@gmail.com}} ~ 
    \href{https://www.linkedin.com/feed/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}\resumeSubHeadingListStart
\resumeItem{Highly motivated Junior Full Stack Developer with a strong academic background in Computer Science seeking a challenging role at Datamixis. Proven ability in Core Java/J2EE, HTML/CSS, Jersey, SQL, PL/SQL, and Oracle Database. Eager to contribute to a dynamic team and leverage skills to deliver innovative solutions.}
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}\resumeSubHeadingListStart
\resumeSubheading{sdhfkljsdahfjksha}{\textbf{jhdkljfhkljshdfkj}}{jhdfjklhasjkhdfkljhasd}{hkdjhfsha}
\resumeItemListStart
\resumeItem{hjksdfhkjshdfkjhasdjkfhkjasdhfkjasdhfkljsdhakfbksdjahfjksdh}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}\resumeSubHeadingListStart
\resumeSubheading{Example Company}{\textbf{Example City, MI}}{Software Engineer}{2021-2023}
\resumeItemListStart
\resumeItem{Developed and maintained 3 key features using Core Java/J2EE, resulting in a 15\% increase in application performance.}
\resumeItem{Improved database efficiency by 10\% through optimized SQL queries and PL/SQL procedures for Oracle Database.}
\resumeItem{Collaborated with cross-functional teams to implement new functionalities, consistently meeting deadlines.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{E-commerce Platform Development}}{\textit{2022}}
\resumeItemListStart
\resumeItem{Developed a robust e-commerce platform using Core Java/J2EE, Jersey RESTful services, and an Oracle database backend.}
\resumeItem{Implemented a responsive user interface with HTML, CSS, and Javascript, enhancing user experience and driving a 20\% increase in sales conversion rates.}
\resumeItem{Successfully integrated a third-party payment gateway, resulting in a seamless and secure checkout process for customers.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Data Analytics Dashboard}}{\textit{2021}}
\resumeItemListStart
\resumeItem{Designed and developed a data analytics dashboard using Java, SQL, and HTML for visualizing key performance indicators.}
\resumeItem{Improved data analysis efficiency by 25\% through optimized query design and data processing techniques.}
\resumeItem{Presented findings to stakeholders, leading to data-driven decision making improving business operations by 10\%.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Inventory Management System}}{\textit{2023}}
\resumeItemListStart
\resumeItem{Developed an inventory management system utilizing Core Java, Jersey, and an Oracle database, improving inventory accuracy by 15\%.}
\resumeItem{Implemented features for real-time tracking and reporting, enhancing stock control and reducing waste by 5\%.}
\resumeItem{Integrated system with existing ERP software via SQL and PL/SQL, streamlining operations and improving data consistency.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SKILLS}}}\resumeSubHeadingListStart
\resumeItem{\textbf{jksdfhjksadhfk:} hkjdfkjashdfjkhds}
\resumeSubHeadingListEnd\vspace{-10pt}
\end{document}