
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont sjdhfl;kjasdlj}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 9375678888 ~ \href{mailto:testing@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{testing@gmail.com}} ~ 
    \href{https://www.linkedin.com/feed/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}


\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}
\resumeSubHeadingListStart

\resumeItem{Senior Engineer with 4+ years of experience in building scalable, resilient distributed systems using Java, Spring Boot, and Azure. Proven ability to design REST APIs, implement DevOps practices, and mentor engineering teams.  Passionate about delivering high-quality, low-maintenance applications.}
\resumeSubHeadingListEnd
\vspace{-18pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}
\resumeSubHeadingListStart
\resumeSubheading{sdhfkljsdahfjksha}{\textbf{jhdkljfhkljshdfkj}}{jhdfjklhasjkhdfkljhasd}{hkdjhfsha}
\resumeItemListStart
\resumeItem{hjksdfhkjshdfkjhasdjkfhkjasdhfkjasdhfkljsdhakfbksdjahfjksdh}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-18pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}
\resumeSubHeadingListStart
\resumeSubheading{Acme Corporation}{\textbf{San Francisco, CA}}{Senior Software Engineer}{2020-Present}
\resumeItemListStart
\resumeItem{Designed and implemented 3 microservices using Spring Boot, resulting in a 20\% increase in application performance.}
\resumeItem{Led the migration of 2 legacy applications to Azure, reducing infrastructure costs by 15\%.}
\resumeItem{Mentored junior engineers in best practices for software development and DevOps.}
\resumeItem{Improved code quality by 10\% through implementing rigorous code reviews and automated testing.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-17pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{GEICO Customer Portal Redesign}}{\textit{2022-2023}}
\resumeItemListStart
\resumeItem{Redesigned the GEICO customer portal using React and Node.js, improving user experience by 30\% (measured by task completion time).}
\resumeItem{Implemented a new authentication system using OAuth 2.0, increasing security by 25\% (reduced successful breaches by 25\%).}
\resumeItem{Integrated with Azure Active Directory for seamless user login and authorization.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Scalable Claims Processing System}}{\textit{2021-2022}}
\resumeItemListStart
\resumeItem{Developed a highly scalable claims processing system using Java, Spring Boot, and Kubernetes, handling a 40\% increase in claims volume.}
\resumeItem{Implemented continuous integration and continuous deployment (CI/CD) pipelines using Azure DevOps, reducing deployment time by 50\%.}
\resumeItem{Improved system reliability by 20\% through implementing robust error handling and monitoring.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Secure API Gateway}}{\textit{2020-2021}}
\resumeItemListStart
\resumeItem{Designed and implemented a secure API gateway using Nginx and Kong, protecting 100+ APIs from unauthorized access.}
\resumeItem{Implemented rate limiting and request filtering to prevent denial-of-service attacks.}
\resumeItem{Integrated with Azure Monitor for real-time monitoring and alerting.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-17pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SKILLS}}}
\resumeSubHeadingListStart
\resumeItem{\textbf{jksdfhjksadhfk:} hkjdfkjashdfjkhds}
\resumeSubHeadingListEnd
\vspace{-10pt}
\end{document}