
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\ \textit{\small#3} & \textit{\small #4} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont Sanaharika Thallada}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 217-775-5653 ~ \href{mailto:sanaharikathallada@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{sanaharikathallada@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/yashwanthtirupati/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}\resumeSubHeadingListStart
\resumeItem{Full-stack Java developer with proven experience in software development, user requirement collaboration, and quality assurance.}
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}\resumeSubHeadingListStart
\resumeSubheading{Saint Louis University}{\textbf{Saint Louis, Missouri}}{Master of Science, Information Systems}{Aug 2023 – May2025}
\resumeItemListStart
\resumeItem{CGPA: 3.63/4.0}
\resumeItem{Coursework: Mobile \&Web App Development, Data Visualization \& Analysis, AWS, Statistics, Tech\& Start-ups}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}\resumeSubHeadingListStart
\resumeSubheading{Cognizant Technology Solutions | Titan}{\textbf{Hyderabad}}{Full-Stack Java Developer}{Aug 2020 – Jul 2023}
\resumeItemListStart
\resumeItem{Developed and implemented high-quality, maintainable Java code for multiple features, resulting in a 15\% increase in application performance.}
\resumeItem{Collaborated with stakeholders to define user requirements, incorporating feedback to improve designs and fix issues, leading to a 10\% reduction in bug reports.}
\resumeItem{Applied debugging tools and telemetry to proactively identify and resolve issues, improving system stability and reducing downtime by 8\%.}
\resumeItemListEnd
\resumeSubheading{Cognizant Technology Solutions}{\textbf{Pune, Maharastra}}{Intern – Programmer Analyst}{Jan 2020 – May 2020}
\resumeItemListStart
\resumeItem{Contributed to software development projects, gaining hands-on experience in Java programming and agile methodologies.}
\resumeItem{Assisted senior engineers in testing and debugging code, contributing to the successful launch of a new product feature.}
\resumeItem{Learned and applied best practices for software development, security, and scalability.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Secure Cloud-Based Application}}{\textit{2023-2024}}
\resumeItemListStart
\resumeItem{Designed and developed a secure, scalable cloud-based application using Java and Spring Boot, achieving 99.9\% uptime.}
\resumeItem{Implemented robust security measures to protect sensitive data, exceeding industry best practices for data privacy and security.}
\resumeItem{Collaborated with a team of engineers to deliver the project on time and within budget, resulting in positive customer feedback and a 20\% increase in user engagement.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{AI-Powered Customer Support System}}{\textit{2022-2023}}
\resumeItemListStart
\resumeItem{Developed an AI-powered customer support system using machine learning algorithms, improving customer satisfaction by 15\%.}
\resumeItem{Integrated the system with existing CRM and ticketing systems, streamlining workflows and reducing response times by 20\%.}
\resumeItem{Optimized the system's performance to handle a large volume of requests, ensuring scalability and reliability.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Microservice Architecture for E-commerce Platform}}{\textit{2022}}
\resumeItemListStart
\resumeItem{Migrated a monolithic e-commerce platform to a microservice architecture, improving scalability and maintainability.}
\resumeItem{Implemented continuous integration and continuous delivery (CI/CD) pipelines to automate the deployment process.}
\resumeItem{Improved application performance and reduced infrastructure costs by 10\% through efficient resource utilization.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SKILLS}}}\resumeSubHeadingListStart
\resumeItem{\textbf{Languages \& Frameworks:} Java, C, C++, Spring Boot, Hibernate, Angular2/4/8, React, Node.js, JSP, Servlets, MVC}\vspace{-7pt}
\resumeItem{\textbf{Frontend:} HTML5, CSS3, JavaScript, jQuery, JSON, XML, XSLT}\vspace{-7pt}
\resumeItem{\textbf{Web Services:} REST , SOAP}\vspace{-7pt}
\resumeItem{\textbf{Cloud \&DevOps:} AWS, Azure, Docker, Google cloud,}\vspace{-7pt}
\resumeItem{\textbf{Tools:} Jira, Confluence, GitHub,GitLab, Postman, Elasticsearch}\vspace{-7pt}
\resumeItem{\textbf{Database:} MySQL}\vspace{-7pt}
\resumeItem{\textbf{Messaging Queues:} ActiveMQ, RabbitMQ}\vspace{-7pt}
\resumeItem{\textbf{Security:} OAuth2, JWT, Spring Security}
\resumeSubHeadingListEnd\vspace{-10pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{CERTIFICATIONS ( UDEMY)}}}
\resumeItemListStart
\resumeItem{Agile Project Management}
\resumeItem{Relational Database Design}
\resumeItem{Responsive Web Design}
\resumeItem{Java Database Connection}
\resumeItem{Maven Crash Course}
\resumeItem{Spring Framework}
\resumeItem{Build Java app with Spring MVC}
\resumeItemListEnd
\vspace{-10pt}
\end{document}