
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\ \textit{\small#3} & \textit{\small #4} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont Sanaharika Thallada}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 217-775-5653 ~ \href{mailto:sanaharikathallada@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{sanaharikathallada@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/yashwanthtirupati/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}\resumeSubHeadingListStart
\resumeItem{Highly motivated and results-oriented Full-Stack Java Developer with 3+ years of experience in software development, seeking to leverage expertise in Python and C++ to design and develop high-performance Python APIs for NVIDIA's math libraries.  Proven ability to develop, debug, and optimize applications on parallel computing platforms, contributing to improved user experiences and performance.  Strong understanding of fundamental numerical methods and agile development methodologies.}
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}\resumeSubHeadingListStart
\resumeSubheading{Saint Louis University}{\textbf{Saint Louis, Missouri}}{Master of Science, Information Systems}{Aug 2023 – May2025}
\resumeItemListStart
\resumeItem{CGPA: 3.63/4.0}
\resumeItem{Coursework: Mobile \&Web App Development, Data Visualization \& Analysis, AWS, Statistics, Tech\& Start-ups}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}\resumeSubHeadingListStart
\resumeSubheading{Cognizant Technology Solutions | Titan}{\textbf{Hyderabad}}{Full-Stack Java Developer}{Aug 2020 – Jul 2023}
\resumeItemListStart
\resumeItem{Developed and maintained high-performance Java applications, improving efficiency by 15\%.}
\resumeItem{Collaborated with cross-functional teams to deliver projects on time and within budget.}
\resumeItem{Implemented innovative solutions using cutting-edge technologies, exceeding client expectations.}
\resumeItemListEnd
\resumeSubheading{Cognizant Technology Solutions}{\textbf{Pune, Maharastra}}{Intern – Programmer Analyst}{Jan 2020 – May 2020}
\resumeItemListStart
\resumeItem{Assisted senior developers in the design and implementation of software modules.}
\resumeItem{Contributed to the testing and debugging of applications, improving overall software quality.}
\resumeItem{Gained hands-on experience in various programming languages and development methodologies.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{High-Performance Linear Algebra Library API}}{\textit{Jan 2022 - Jun 2022}}
\resumeItemListStart
\resumeItem{Designed and implemented Python APIs for linear algebra operations using NumPy and SciPy.}
\resumeItem{Optimized API performance for various CPU and GPU architectures, achieving a 20\% speedup.}
\resumeItem{Integrated the APIs into existing machine learning frameworks, improving ease of use for developers.}
\resumeItem{Performed rigorous testing and benchmarking to ensure accuracy and reliability.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{GPU-Accelerated Numerical Computation Library}}{\textit{Sep 2021 - Mar 2022}}
\resumeItemListStart
\resumeItem{Developed and optimized Python APIs for GPU-accelerated numerical computations using CUDA.}
\resumeItem{Improved performance of existing algorithms by leveraging parallel processing capabilities.}
\resumeItem{Collaborated with researchers to integrate the library into their scientific computing workflows.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Python API for Deep Learning Framework Integration}}{\textit{Oct 2022 - Apr 2023}}
\resumeItemListStart
\resumeItem{Created Python APIs to seamlessly integrate NVIDIA math libraries with popular deep learning frameworks such as PyTorch and TensorFlow.}
\resumeItem{Developed comprehensive documentation and tutorials to enhance user experience and adoption rate.}
\resumeItem{Consistently monitored and improved API performance based on user feedback and performance benchmarks.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SKILLS}}}\resumeSubHeadingListStart
\resumeItem{\textbf{Languages \& Frameworks:} Java, C, C++, Spring Boot, Hibernate, Angular2/4/8, React, Node.js, JSP, Servlets, MVC}\vspace{-7pt}
\resumeItem{\textbf{Frontend:} HTML5, CSS3, JavaScript, jQuery, JSON, XML, XSLT}\vspace{-7pt}
\resumeItem{\textbf{Web Services:} REST , SOAP}\vspace{-7pt}
\resumeItem{\textbf{Cloud \&DevOps:} AWS, Azure, Docker, Google cloud,}\vspace{-7pt}
\resumeItem{\textbf{Tools:} Jira, Confluence, GitHub,GitLab, Postman, Elasticsearch}
\resumeSubHeadingListEnd\vspace{-10pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{CERTIFICATIONS (UDEMY)}}}
\resumeItemListStart
\resumeItem{Agile Project Management}
\vspace{-8pt}
\resumeItem{Relational Database Design}
\vspace{-8pt}
\resumeItem{Responsive Web Design}
\vspace{-8pt}
\resumeItemListEnd
\vspace{-8pt}
\end{document}