
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\ \textit{\small#3} & \textit{\small #4} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont Sanaharika Thallada}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 217-775-5653 ~ \href{mailto:sanaharikathallada@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{sanaharikathallada@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/yashwanthtirupati/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}\resumeSubHeadingListStart
\resumeItem{Highly motivated and results-oriented Full-Stack Java Developer with 3+ years of experience seeking a Junior Software Engineer position. Proven ability to design, develop, and deploy robust software solutions.  Proficient in Java and eager to leverage skills in Python, C++, and MATLAB in a challenging, mission-focused environment.  Dedicated to contributing to critical national security operations.}
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}\resumeSubHeadingListStart
\resumeSubheading{Saint Louis University}{\textbf{Saint Louis, Missouri}}{Master of Science, Information Systems}{Aug 2023 – May2025}
\resumeItemListStart
\resumeItem{CGPA: 3.63/4.0}
\resumeItem{Coursework: Mobile \&Web App Development, Data Visualization \& Analysis, AWS, Statistics, Tech\& Start-ups}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}\resumeSubHeadingListStart
\resumeSubheading{Cognizant Technology Solutions | Titan}{\textbf{Hyderabad}}{Full-Stack Java Developer}{Aug 2020 – Jul 2023}
\resumeItemListStart
\resumeItem{Designed and developed key features for a high-traffic web application using Java, Spring Boot, and React.}
\resumeItem{Improved application performance by 20\% through code optimization and database tuning.}
\resumeItem{Collaborated with cross-functional teams to deliver projects on time and within budget.}
\resumeItem{Successfully implemented a new microservice architecture resulting in improved scalability and maintainability.}
\resumeItemListEnd
\resumeSubheading{Cognizant Technology Solutions}{\textbf{Pune, Maharastra}}{Intern – Programmer Analyst}{Jan 2020 – May 2020}
\resumeItemListStart
\resumeItem{Developed and implemented algorithms for data processing and analysis.}
\resumeItem{Contributed to the improvement of existing software applications through bug fixes and enhancements.}
\resumeItem{Gained experience in software development methodologies and best practices.}
\resumeItem{Successfully completed a capstone project involving the development of a mobile application.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Mission-Critical Data Processing System}}{\textit{Jan 2022 - Jun 2022}}
\resumeItemListStart
\resumeItem{Developed a high-throughput data processing system using Python and C++ to handle large volumes of sensitive data.}
\resumeItem{Implemented robust error handling and security measures to ensure data integrity and confidentiality.}
\resumeItem{Optimized the system for performance and scalability to meet demanding operational requirements.}
\resumeItem{Successfully integrated the system with existing infrastructure and tools.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Real-time Signal Processing Application}}{\textit{Oct 2021 - Mar 2022}}
\resumeItemListStart
\resumeItem{Designed and implemented a real-time signal processing application using MATLAB for analyzing and interpreting complex signals.}
\resumeItem{Developed algorithms for noise reduction, feature extraction, and classification using DSP techniques.}
\resumeItem{Integrated the application with various hardware components and sensors.}
\resumeItem{Achieved a significant improvement in signal processing accuracy and speed.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Secure Data Transport System}}{\textit{Aug 2023 - Dec 2023}}
\resumeItemListStart
\resumeItem{Developed a secure data transport system using Python and Docker to ensure the confidentiality and integrity of sensitive data.}
\resumeItem{Implemented encryption and authentication mechanisms to protect data from unauthorized access.}
\resumeItem{Designed and implemented a robust logging and monitoring system to track data transfers and identify potential security breaches.}
\resumeItem{Successfully deployed the system to a cloud-based environment.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SKILLS}}}\resumeSubHeadingListStart
\resumeItem{\textbf{Languages \& Frameworks:} Java, C, C++, Spring Boot, Hibernate, Angular2/4/8, React, Node.js, JSP}\vspace{-7pt}
\resumeItem{\textbf{Frontend:} HTML5, CSS3, JavaScript, jQuery, JSON, XML, XSLT}\vspace{-7pt}
\resumeItem{\textbf{Web Services:} REST , SOAP}\vspace{-7pt}
\resumeItem{\textbf{Cloud \&DevOps:} AWS, Azure, Docker, Google cloud,}\vspace{-7pt}
\resumeItem{\textbf{Tools:} Jira, Confluence, GitHub,GitLab, Postman, Elasticsearch}\vspace{-7pt}
\resumeItem{\textbf{Database:} :MySQL}\vspace{-7pt}
\resumeItem{\textbf{Messaging Queues:} ActiveMQ, RabbitMQ}\vspace{-7pt}
\resumeItem{\textbf{Security:} OAuth2, JWT, Spring Security}
\resumeSubHeadingListEnd\vspace{-10pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{CERTIFICATIONS (UDEMY)}}}
\resumeItemListStart
\resumeItem{Agile Project Management}
\vspace{-8pt}
\resumeItem{Relational Database Design}
\vspace{-8pt}
\resumeItem{Responsive Web Design}
\vspace{-8pt}
\resumeItemListEnd
\vspace{-8pt}
\end{document}