
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\ \textit{\small#3} & \textit{\small #4} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont Sanaharika Thallada}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 217-775-5653 ~ \href{mailto:sanaharikathallada@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{sanaharikathallada@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/yashwanthtirupati/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}\resumeSubHeadingListStart
\resumeItem{Full-stack engineer with experience building AI-driven products. Proven ability to design, develop, and deploy features using Python, React, and TypeScript.}
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}\resumeSubHeadingListStart
\resumeSubheading{Saint Louis University}{\textbf{Saint Louis, Missouri}}{Master of Science, Information Systems}{Aug 2023 – May2025}
\resumeItemListStart
\resumeItem{CGPA: 3.63/4.0}
\resumeItem{Coursework: Mobile \&Web App Development, Data Visualization \& Analysis, AWS, Statistics, Tech\& Start-ups}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}\resumeSubHeadingListStart
\resumeSubheading{Cognizant Technology Solutions | Titan}{\textbf{Hyderabad}}{Full-Stack Java Developer}{Aug 2020 – Jul 2023}
\resumeItemListStart
\resumeItem{Developed and maintained full-stack features for complex applications, resulting in a 15\% improvement in user engagement.}
\resumeItem{Designed and implemented RESTful APIs using Spring Boot, improving data transfer efficiency by 20\%.}
\resumeItem{Collaborated with cross-functional teams to deliver high-quality software solutions on time and within budget.}
\resumeItem{Utilized Agile methodologies to manage sprints and deliver incremental value.}
\resumeItemListEnd
\resumeSubheading{Cognizant Technology Solutions}{\textbf{Pune, Maharastra}}{Intern – Programmer Analyst}{Jan 2020 – May 2020}
\resumeItemListStart
\resumeItem{Contributed to the development of a key module for a large-scale enterprise application, enhancing system performance by 10\%.}
\resumeItem{Assisted senior developers in debugging and troubleshooting complex issues, resolving critical bugs and improving application stability.}
\resumeItem{Gained practical experience in various aspects of software development, including design, coding, testing, and deployment.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{AI-Powered Workflow Automation Platform}}{\textit{March 2023 - October 2023}}
\resumeItemListStart
\resumeItem{Developed a Python-based backend API using FastAPI to handle complex data processing and AI model integration.}
\resumeItem{Built a React and TypeScript frontend to provide a user-friendly interface for interacting with the AI-powered workflow automation platform.}
\resumeItem{Integrated an LLM for natural language processing, improving user efficiency by 25\% as measured by task completion time.}
\resumeItem{Deployed the application to a containerized environment using Docker and Kubernetes, ensuring high availability and scalability.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Intelligent Data Processing System}}{\textit{July 2022 - December 2022}}
\resumeItemListStart
\resumeItem{Designed and implemented a robust data pipeline using Python and PostgreSQL for efficient data ingestion, transformation, and loading.}
\resumeItem{Developed a GUI application (React/TypeScript) to visualize and analyze the processed data, enabling intuitive data exploration and improved decision-making.}
\resumeItem{Implemented ETL processes for efficient data integration, reducing processing time by 30\%.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Recommendation Engine}}{\textit{October 2022 - March 2023}}
\resumeItemListStart
\resumeItem{Built a recommendation engine using Python and Redis for a real-time, high-volume application that recommends products to users.}
\resumeItem{Improved product recommendations by 10\% through the implementation of collaborative filtering algorithms. }
\resumeItem{Increased user engagement by 15\% by personalizing the user experience with targeted recommendations.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SKILLS}}}\resumeSubHeadingListStart
\resumeItem{\textbf{Languages \& Frameworks:} Java, C, C++, Spring Boot, Hibernate, Angular2/4/8, React, Node.js, JSP, Servlets, MVC}\vspace{-7pt}
\resumeItem{\textbf{Frontend:} HTML5, CSS3, JavaScript, jQuery, JSON, XML, XSLT}\vspace{-7pt}
\resumeItem{\textbf{Web Services:} REST , SOAP}\vspace{-7pt}
\resumeItem{\textbf{Cloud \&DevOps:} AWS, Azure, Docker, Google cloud,}\vspace{-7pt}
\resumeItem{\textbf{Tools:} Jira, Confluence, GitHub,GitLab, Postman, Elasticsearch}\vspace{-7pt}
\resumeItem{\textbf{Database:} MySQL}\vspace{-7pt}
\resumeItem{\textbf{Messaging Queues:} ActiveMQ, RabbitMQ}\vspace{-7pt}
\resumeItem{\textbf{Security:} OAuth2, JWT, Spring Security}
\resumeSubHeadingListEnd\vspace{-10pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{CERTIFICATIONS ( UDEMY)}}}
\resumeItemListStart
\resumeItem{Agile Project Management}
\resumeItem{Relational Database Design}
\resumeItem{Responsive Web Design}
\resumeItem{Java Database Connection}
\resumeItem{Maven Crash Course}
\resumeItem{Spring Framework}
\resumeItem{Build Java app with Spring MVC}
\resumeItemListEnd
\vspace{-10pt}
\end{document}