
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont sjdhfl;kjasdlj}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 9375678888 ~ \href{mailto:testing@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{testing@gmail.com}} ~ 
    \href{https://www.linkedin.com/feed/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}


\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}
\resumeSubHeadingListStart

\resumeItem{Senior Engineer with 4+ years' experience building scalable, resilient distributed systems using Java, Spring Boot, and Azure. Proven ability to design REST APIs, implement DevOps practices, and mentor engineering teams. Expertise in microservices architecture and cloud technologies.}
\resumeSubHeadingListEnd
\vspace{-18pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}
\resumeSubHeadingListStart
\resumeSubheading{sdhfkljsdahfjksha}{\textbf{jhdkljfhkljshdfkj}}{jhdfjklhasjkhdfkljhasd}{hkdjhfsha}
\resumeItemListStart
\resumeItem{hjksdfhkjshdfkjhasdjkfhkjasdhfkjasdhfkljsdhakfbksdjahfjksdh}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-18pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}
\resumeSubHeadingListStart
\resumeSubheading{Acme Corporation}{\textbf{New York, NY}}{Senior Software Engineer}{2020-Present}
\resumeItemListStart
\resumeItem{Designed and implemented 3 microservices using Spring Boot, resulting in a 20\% reduction in system latency.}
\resumeItem{Led a team of 4 engineers in migrating a legacy application to Azure, improving scalability by 50\%.}
\resumeItem{Mentored junior engineers on best practices in software development and DevOps, leading to a 15\% increase in team efficiency.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-17pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{GEICO Claims Processing System Modernization}}{\textit{2022-2023}}
\resumeItemListStart
\resumeItem{Migrated legacy claims processing system to a microservices architecture on Azure, improving processing speed by 30\% and reducing errors by 15\%.}
\resumeItem{Developed RESTful APIs for seamless integration with other GEICO systems, enhancing customer experience and operational efficiency.}
\resumeItem{Implemented robust security protocols (Active Directory, SAML, OAuth) to protect sensitive customer data, ensuring compliance with industry standards.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{High-Availability Web Application for Customer Portal}}{\textit{2021-2022}}
\resumeItemListStart
\resumeItem{Architected and implemented a high-availability web application using Java, Spring Boot, and Kubernetes on Azure.}
\resumeItem{Improved application uptime by 99.99\%, exceeding customer expectations for service reliability.}
\resumeItem{Implemented comprehensive application monitoring and performance assessment tools, enabling proactive issue detection and resolution.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{DevOps Pipeline Implementation for Continuous Delivery}}{\textit{2020-2021}}
\resumeItemListStart
\resumeItem{Implemented a CI/CD pipeline using Azure DevOps, reducing deployment time by 75\% and improving software release frequency.}
\resumeItem{Utilized infrastructure as code (IaC) to automate infrastructure provisioning and management, enhancing scalability and reducing operational overhead.}
\resumeItem{Developed and implemented automated testing strategies, resulting in a 20\% reduction in production bugs.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-17pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SKILLS}}}
\resumeSubHeadingListStart
\resumeItem{\textbf{jksdfhjksadhfk:} hkjdfkjashdfjkhds}
\resumeSubHeadingListEnd
\vspace{-10pt}
\end{document}