
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\ \textit{\small#3} & \textit{\small #4} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont Sanaharika Thallada}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 217-775-5653 ~ \href{mailto:sanaharikathallada@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{sanaharikathallada@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/yashwanthtirupati/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}\resumeSubHeadingListStart
\resumeItem{Full-stack developer proficient in C\#, Angular, and cloud technologies seeking to design, develop, and deploy high-quality, scalable applications.}
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}\resumeSubHeadingListStart
\resumeSubheading{Saint Louis University}{\textbf{Saint Louis, Missouri}}{Master of Science, Information Systems}{Aug 2023 – May2025}
\resumeItemListStart
\resumeItem{CGPA: 3.63/4.0}
\resumeItem{Coursework: Mobile \&Web App Development, Data Visualization \& Analysis, AWS, Statistics, Tech\& Start-ups}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-18pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}\resumeSubHeadingListStart
\resumeSubheading{Cognizant Technology Solutions | Titan}{\textbf{Hyderabad}}{Full-Stack Java Developer}{Aug 2020 – Jul 2023}
\resumeItemListStart
\resumeItem{Developed and maintained high-performance, scalable applications using Java, contributing to improved system reliability and efficiency.}
\resumeItem{Designed and implemented RESTful APIs, enhancing system interoperability and data exchange capabilities.}
\resumeItem{Collaborated with cross-functional teams to deliver new features, ensuring timely project completion and alignment with business goals.}
\resumeItemListEnd
\resumeSubheading{Cognizant Technology Solutions}{\textbf{Pune, Maharastra}}{Intern – Programmer Analyst}{Jan 2020 – May 2020}
\resumeItemListStart
\resumeItem{Contributed to the development of a key application feature, resulting in a 15\% improvement in user engagement.}
\resumeItem{Successfully debugged and resolved critical production issues, minimizing downtime and improving system stability.}
\resumeItem{Applied agile methodologies to deliver projects on time and within budget.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Cloud-Based DevOps Automation Platform}}{\textit{March 2023 - October 2023}}
\resumeItemListStart
\resumeItem{Designed and implemented a scalable, cloud-based platform using C\# and .NET for automating DevOps workflows, resulting in a 20\% reduction in infrastructure management time.}
\resumeItem{Developed a user-friendly interface using Angular 11+, improving user experience and enhancing team collaboration.}
\resumeItem{Integrated with AWS cloud services, ensuring high availability and scalability of the platform.}
\resumeItem{Implemented CI/CD pipelines to automate the deployment process, reducing deployment time by 50\%.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Microservices-Based E-commerce Application}}{\textit{June 2022 - December 2022}}
\resumeItemListStart
\resumeItem{Developed a robust and scalable e-commerce application using microservices architecture with C\# and .NET, improving application performance by 30\%.}
\resumeItem{Built responsive and user-friendly front-end interfaces using Angular 11+, enhancing customer experience and conversion rates.}
\resumeItem{Implemented containerization and orchestration using Docker and Kubernetes to manage deployments and scale applications efficiently.}
\resumeItem{Integrated with various payment gateways and shipping providers to streamline the checkout process.}
\resumeItemListEnd\vspace{-6pt}
\resumeProjectHeading{\textbf{Secure and Scalable Web Application}}{\textit{January 2022 - May 2022}}
\resumeItemListStart
\resumeItem{Developed a secure and scalable web application using C\#, .NET, and Angular 11+, improving system security by 10\% and achieving 99.9\% uptime.}
\resumeItem{Implemented robust security measures, including authentication and authorization, to protect sensitive data and prevent unauthorized access.}
\resumeItem{Optimized application performance through code refactoring and database tuning, resulting in faster load times and improved user experience.}
\resumeItem{Successfully deployed the application to AWS cloud infrastructure, ensuring high availability and reliability.}
\resumeItemListEnd
\resumeSubHeadingListEnd\vspace{-17pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SKILLS}}}\resumeSubHeadingListStart
\resumeItem{\textbf{Languages \& Frameworks:} Java, C, C++, Spring Boot, Hibernate, Angular2/4/8, React, Node.js, JSP, Servlets, MVC}\vspace{-7pt}
\resumeItem{\textbf{Frontend:} HTML5, CSS3, JavaScript, jQuery, JSON, XML, XSLT}\vspace{-7pt}
\resumeItem{\textbf{Web Services:} REST , SOAP}\vspace{-7pt}
\resumeItem{\textbf{Cloud \&DevOps:} AWS, Azure, Docker, Google cloud,}\vspace{-7pt}
\resumeItem{\textbf{Tools:} Jira, Confluence, GitHub,GitLab, Postman, Elasticsearch}\vspace{-7pt}
\resumeItem{\textbf{Database:} MySQL}\vspace{-7pt}
\resumeItem{\textbf{Messaging Queues:} ActiveMQ, RabbitMQ}\vspace{-7pt}
\resumeItem{\textbf{Security:} OAuth2, JWT, Spring Security}
\resumeSubHeadingListEnd\vspace{-10pt}
\section{{\fontsize{9pt}{20pt}\selectfont \textbf{CERTIFICATIONS ( UDEMY)}}}
\resumeItemListStart
\resumeItem{Agile Project Management}
\vspace{-10pt}
\resumeItem{Relational Database Design}
\vspace{-10pt}
\resumeItem{Responsive Web Design}
\vspace{-10pt}
\resumeItem{Java Database Connection}
\vspace{-10pt}
\resumeItem{Maven Crash Course}
\vspace{-10pt}
\resumeItem{Spring Framework}
\vspace{-10pt}
\resumeItem{Build Java app with Spring MVC}
\vspace{-10pt}
\resumeItemListEnd
\vspace{-10pt}
\end{document}